---
output:
  word_document: default
  html_document: default
---
# BAN 508- Module 2
## Multiple Linear Regressions
### Allison Kornegay


```{r}
library(tidyverse)
library(GGally)
library(MASS)
library(car)
library(gridExtra)
```

```{r}
library(readr)
bike <- read_csv("hour.csv")
```
```{r}
bike = bike %>% mutate(season = as_factor(as.character(season))) %>%
mutate(season = fct_recode(season,
  "Spring" = "1",
  "Summer" = "2",
  "Fall" = "3",
  "Winter" = "4"))
```

```{r}
bike = bike %>% mutate(yr = as_factor(as.character(yr)))
```

```{r}
bike = bike %>% mutate(mnth = as_factor(as.character(mnth)))
```

```{r}
bike = bike %>% mutate(hr = as_factor(as.character(hr)))
```

```{r}
bike = bike %>% mutate(holiday = as_factor(as.character(holiday))) %>%
mutate(holiday = fct_recode(holiday,
  "NotHoliday" = "0",
  "Holiday" = "1"))
```

```{r}
bike = bike %>% mutate(workingday = as_factor(as.character(workingday))) %>%
mutate(workingday = fct_recode(workingday,
  "NotWorkingDay" = "0",
  "WorkingDay" = "1"))
```

```{r}
bike = bike %>% mutate(weathersit = as_factor(as.character(weathersit))) %>%
mutate(weathersit = fct_recode(weathersit,
  "NoPrecip" = "1",
  "Misty" = "2",
  "LightPrecip" = "3",
  "HeavyPrecip" = "4"))
```

```{r}
bike = bike %>% mutate(weekday = as_factor(as.character(weekday))) %>%
mutate(weekday = fct_recode(weekday,
  "Sunday" = "0",
  "Monday" = "1",
  "Tuesday" = "2",
  "Wednesday" = "3",
  "Thursday" = "4",
  "Friday" = "5",
  "Saturday" = "6"))
```

```{r}
ggcorr(bike, label = "TRUE", label_round = TRUE)
```

# Atemp and temp are seemingly the nost correlated with count.

```{r}
boxplot(count ~ season, bike)
boxplot(count ~ workingday, bike)
boxplot(count ~ holiday, bike)
boxplot(count ~ yr, bike)
boxplot(count ~ mnth, bike)
boxplot(count ~ hr, bike)
boxplot(count ~ weathersit, bike)
boxplot(count ~ weekday, bike)
```
# Bike rentals are more popular in the summer and fall. 
# Bike rentals are more popular during working days.
# Bike rentals are less popular during non holidays.
# Bike rentals have grown from year 1 to 2.
# Bike rentals are more popular during months 5-10.
# Bike rentals are most popular between hours 7-18 (7-6)
# Bike rentals are most popular in no precip or misty weather conditions.
# Bike rentals are most popular on the weekdays.

# All things discovered from the box plots are sensible. Peopl tend to rent bikes to go to work- therefore, it makes perfect sense the popular days are weekdays between the hours of 7-6. Obviously, the better the weather and the warmer it is outside, people will ride bikes. 


```{r}
bike2 = bike %>% dplyr::select(-c(instant, dteday, registered, casual))
```



```{r}
allmod = allmod = lm(count ~., bike2)
summary(allmod)

```



```{r}
emptymod = lm(count ~1, bike2) 
summary(emptymod)
```



```{r}
forwardmod = stepAIC(emptymod, direction = "forward",
scope=list(upper=allmod,lower=emptymod),
 trace = TRUE)
summary(forwardmod)
```

```{r}
backmod = stepAIC(emptymod, direction = "backward",
scope=list(upper=allmod,lower=emptymod),
 trace = TRUE)
summary(backmod)
```
# Forward model uses  atemp + yr + weathersit + season + mnth + hum + weekday + holiday + windspeed + temp, all oh which make sense, inutitivley. 

# working day likely has an exact correlation with holiday non holiday.

# The forwads and backwards model were slightly different. I would be skeptical to use this model because the AIC values are still extremely high and the R2 value is not great. However, that could be partly due to user error. I felt as if the models should've been suited for better use and I struggled with this assignment.Unfortunatley, I can't start from scratch and redo the assignment at this point, but I will go back and re-watch all of the lecture materials and sample datasets.
